### 2019-09-13 README.Rmd
Made dits to step 2 sections of README and vignette

### Step 2: Perform individual enrichment analysis

In this step we will use the *pathEnrich* function to identify KEGG pathways that are enriched (i.e. over-represented) based on two gene lists of interest. The ENTREZ gene IDs. User gene lists must also be character vectors and be formatted as ENTREZ gene IDs. The *clusterProfiler* offers a nice function (*bitr*) that maps gene symbols and Ensembl IDs to ENTREZ gene IDs, and an example can be seen in their [vignette](https://yulab-smu.github.io/clusterProfiler-book/chapter5.html#supported-organisms).

@@

This function may not always use the complete list of genes provided 
by the user. Specifically, it will only use the genes from the list provided that are also in
the most current species list pulled from the KEGG REST API using *get_kegg*, or from the older KEGG data loaded by the user from a 
previous *get_kegg* call. The *pathEnrich* function should be run at least twice, once for the genes of interest in list 1 and once for the genes of interest in list2. Each *pathEnrich* call generates a data frame summarizing the results of an enrichment analysis in which a Fisher's Exact test is used to identify which KEGG pathways are enriched by the user's list of interesting genes with respect to background
(universe), and a p-value is calculated using a hypergeometric distribution (Formula 1). P-values are adjusted for multiple comparisons by controlling the False Discovery Rate (FDR) at 0.05.

Formula 1:

$$ P = 1-\sum_{i=0}^{k-1} \frac{ \binom{m} {i} \binom{N-M} {n-i} } {\binom{N} {n} } $$

where N is the total number of genes in the background, M is the number of genes within that background that also in the gene set of interest, n is the size of the list of genes of interest and k is the number of genes within that are in the background. The background (universe) by default is all the genes that have annotation.

@@

```{r pathEnrich_kable, warning=FALSE, echo=FALSE}
knitr::kable(head(list1_pe),
             caption = "Table 2. Head of list1_pe data frame generated using pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

>>>>

### Step 2: Perform enrichment analysis of individual gene sets

In this step we will use the *pathEnrich* function to identify KEGG pathways that are enriched (i.e. over-represented) based on a gene list of interest. User gene lists must also be character vectors and be formatted as ENTREZ gene IDs. The *clusterProfiler* package offers a nice function (*bitr*) that maps gene symbols and Ensembl IDs to ENTREZ gene IDs, and an example can be seen in their [vignette](https://yulab-smu.github.io/clusterProfiler-book/chapter5.html#supported-organisms).

@@

This function may not always use the complete list of genes provided 
by the user. Specifically, it will only use the genes from the list provided that are also in
the most current species list pulled from the KEGG REST API using *get_kegg*, or from the older KEGG data loaded by the user from a 
previous *get_kegg* call. The *pathEnrich* function should be run at least twice, once for the genes of interest in list 1 and once for the genes of interest in list2. Each *pathEnrich* call generates a data frame summarizing the results of an enrichment analysis in which a Fisher's Exact test is used to identify which KEGG pathways are enriched within the user's list of interesting genes compared to all genes annotated to a KEGG pathway. P-values from the Fisher's Exact test are adjusted for multiple comparisons by controlling the False Discovery Rate (FDR) at 0.05.

@@

```{r pathEnrich_kable, warning=FALSE, echo=FALSE}
knitr::kable(head(list1_pe),
             caption = "Table 2. First 6 rows of list1_pe data frame generated using pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```
